Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-01 paper.qmd
Updated long edge benchmark values

distance_hist <- ggplot(
  distance_two_curvy_dist, 
  aes(x = as.numeric(bin),
      y = prop)) +
  geom_line() +
  scale_x_continuous(breaks = as.numeric(distance_two_curvy_dist$bin),
                     labels = c(
                       expression(2*a[1]),
                       expression(3*a[1]),
                       expression(4*a[1]),
                       expression(5*a[1]),
                       expression(6*a[1]),
                       expression(7*a[1]),
                       expression(8*a[1])
                     )) +
  geom_vline(xintercept = 3,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 5,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  ylab("Proportion of the number of edges") +
  xlab(expression(d^{(2)})) +
  #ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

@@

benchmark_two_curvy <- 0.42

>>>>

distance_hist <- ggplot(
  distance_two_curvy_dist, 
  aes(x = as.numeric(bin),
      y = prop)) +
  geom_line() +
  scale_x_continuous(breaks = as.numeric(distance_two_curvy_dist$bin),
                     labels = c(
                       expression(2*a[1]),
                       expression(3*a[1]),
                       expression(4*a[1]),
                       expression(5*a[1]),
                       expression(6*a[1]),
                       expression(7*a[1]),
                       expression(8*a[1])
                     )) +
  geom_vline(xintercept = 2,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 5,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  ylab("Proportion of the number of edges") +
  xlab(expression(d^{(2)})) +
  #ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

benchmark_two_curvy <- 2 * bin_width

@@

benchmark_two_curvy <- 5 * bin_width
